### 2012-09-11 inst/examples/debug_uniform.Rmd
Looking into doing integral analytically and quasi-analytically for the uniform case

With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.

``` {r }
pars <- c(r, K)
````

@@

We use Monte Carlo integration over the noise processes to determine the transition matrix.

``` {r beparallel, cache=FALSE}
require(snowfall)
sfInit(parallel=TRUE, cpu=16)
````

``` {r policyscenarios}
scenario <- function(policy_g, policy_m, policy_i){

  z_g <- function() 1+(2*runif(1, 0,  1)-1) * policy_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * policy_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * policy_i

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

@@

```{r deterministic}
pdfn <- function(P, s){
     dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn)
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

>>>>

With parameters

``` {r }
r <- 1
K <- 100
pars <- c(r, K)
````

`r` = `r r` and `K` = `r K`.

@@

@@

```{r deterministic}
pdfn <- function(P, s){
     dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- SDP_uniform(f, pars, x_grid, h_grid, sigma_g=0.5, pdfn, sigma_m=.5, sigma_i=.5)

SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g = 0.5, pdfn)
det <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````
